Vragenlijst thesis evaluatie

### 2015-02-14 doc/template/chap-1.tex
meer papers
referenties bibtex aanvullen

%\chapter{Intoduction to GameTheory}
%\label{cha:1}
\documentclass[10pt]{article}
\begin{document}

In this chapter an introduction to gametheory will be given with the formulas that will be used troughout this paper. We start with the basics of gametheory. People that have a background in gametheory can skip this chapter.

@@

\subsection{Malware}
%Does a company network faces lot of malware? what is the cost ?
Relevant researches:
\begin{itemize}
%
\item 
\end{itemize}

@@

\end{document}

>>>>

\chapter{Intoduction to GameTheory}
\label{cha:1}
%\documentclass[10pt]{article}
%\begin{document}

In this chapter an introduction to gametheory will be given with the formulas that will be used throughout this paper. We start with the basics of gametheory. People that have a background in gametheory can skip this chapter.
\section{Intro to Gametheory}

Game Theory is the study of interactions between independent and self-interested agents. It is a set of tools to analyze situations in which the optimal action for an agent depends on anticipations that form over another agent decision \todo{citatie vanuit wikipedia}. An agent can be either an individual, an animal or an enterprise.  Game theory can be applied on various domains such as politics, economics, biology, sociology.
In game theory studies the strategic interaction between players in a game. A game is played by a number of players and each of these players has actions. These actions are represented by a number indicating their preference.

@@

\subsection{Malware}
%Does a company network faces lot of malware? what is the cost ?
Relevant researches:
\begin{itemize}
%http://ants.iis.sinica.edu.tw/3BkMJ9lTeWXTSrrvNoKNFDxRm3zFwRR/17/04483668.pdf
\item How Viruses and worm can be detected. Difference between UDP en TCP worm propagation
\end{itemize}

@@

%\end{document}
